Optimal (Multiway) Spatial Joins

### 2024-05-26 msj.tex
yufei

The computation of $\J^\catt_{i,j}$ is an instance of H-V $k$-SJ. Specifically, collect the top-edges of all rectangles $r_i \in R_i$ into a set $H$, and collect the left-edges of all rectangles $r_j \in R_j$ into a set $V$. This yields an H-V $k$-SJ problem whose input comprises all the $R_z$ with $z \in [k] \setminus \set{i,j}$, and $H$ and $V$

>>>>

The computation of $\J^\catt_{i,j}$ is an instance of H-V $k$-SJ. Specifically, collect the top-edges of all rectangles $r_i \in R_i$ into a set $H$, and collect the left-edges of all rectangles $r_j \in R_j$ into a set $V$. This yields an H-V $k$-SJ problem whose input comprises all the $R_z$ with $z \in [k] \setminus \set{i,j}$,  $H$, and $V$. Its output includes every $r_z \in R_z$, for $z \in [k] \setminus \set{i,j}$, $h \in H$, and $v \in V$ such that $h \cap v \cap \bigcap_{z \in [k] \setminus \set{i,j}} r_z \ne \emptyset$.
